\documentclass[twocolumn,10pt]{extarticle}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[margin=1cm]{geometry}

% even text columns
\usepackage{balance}

% refs
\usepackage[colorlinks=true,linkcolor=blue,pdftex]{hyperref}

% custom section
\usepackage{titlesec}
\titleformat{\section}{
  \vspace{3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{3pt}]

% custom subsection
\usepackage{titlesec}
\titleformat{\subsection}{
  \vspace{1pt}\scshape\raggedright
}{}{0em}{}[\color{black} \vspace{1pt}]

% --- %

\title{\Huge Dmitry Ulyumdzhiev}


\date{}

\begin{document}

\maketitle

\balance

\thispagestyle{empty}

\section{Social}

\texttt{Codeforces:} \href{https://codeforces.com/profile/Byobe}{\texttt{Byobe}} \\
\texttt{Leetcode:} \href{https://leetcode.com/deadb0d4/}{\texttt{deadb0d4}} \\
\texttt{Telegram:} \href{https://t.me/dulyumdzhiev}{\texttt{dulyumdzhiev}} \\
\texttt{E-mail:} \href{mailto:dulumzhiev@gmail.com}{dulumzhiev [at] gmail [dot] com} \\

{I have this public \href{https://drive.google.com/drive/folders/1NT6w2IOH1FO1XDOfCJ9cktBSh_USbbWq?usp=sharing}{drive folder} with scans of my awards, diplomas and certificates.}

\section{Personal}

\begin{enumerate}
  \item \texttt{Born:} September 26, 1996, Elista, Russia
  \item \texttt{Citizenship:} Russia
  \item \texttt{Ethnicity:} Kalmyk
  \item \texttt{Languages:}
    \begin{enumerate}
      \item Russian (native)
      \item English (\texttt{8.0} IELTS Academic in Fall 2019)
    \end{enumerate}
\end{enumerate}

\section{Selected awards}

\subsection{Mathematical olympiads}
\begin{enumerate}
  \item \textit{Moscow Mathematical Olympiad} \\
    \quad \texttt{First prize, 2014}
  \item \textit{Moscow University Mathematical Olympiad} \\
    \quad \texttt{6th place, 2017}
  \item \textit{International Mathematical Competition} \\
    \quad \texttt{Second prize, 2017}
\end{enumerate}

\subsection{Programming contests}
\begin{enumerate}
  \item \textit{Yandex Programming Contest} \\
    \quad \texttt{Top-21, 100\% solved, November 2019}
  \item \textit{Google Kickstart Round G 2020} \\
    \quad \texttt{Top-46, 100\% solved, October 2020}
\end{enumerate}

\vfill

\section{Education}

\begin{enumerate}
  \item \href{https://www.msu.ru/en/}{Lomonosov Moscow State University} \\
    \quad Master degree in Mathematics, a diploma with honours, 2014-2020
  \item \href{https://yandexdataschool.com}{Yandex School of Data Analysis} \\
    \quad Master’s-level program, a Big Data group, 2017-2019
\end{enumerate}

\section{Experience}

\begin{enumerate}
  \item \textit{Yandex N.V.}, Moscow office \\
    \quad Software Engineer Intern (June 2018 -- Sept. 2018)

    \quad I have been working on recommendation systems without significant progress.
  \item \textit{Yandex N.V.}, Moscow office \\
    \quad Junior software engineer (Nov. 2019 -- Voluntary dismissal in Jan. 2020)

    \quad I have coded the backend part of the New Year Promo microservice based on internal \texttt{C++} frameworks.
  \item \textit{Huawei}, Moscow Research Center \\
    \quad Computer Vision Research Engineer (since Nov. 2020 -- Voluntary dismissal in Feb. 2021)

    \quad I have improved over `SotA` level of industrial anomaly detection using Deep Learning.
  \item \textit{twin3d} \\
    \quad Software Engineer (since Feb. 2021)

    \quad I work on challenging problems in Computer Vision as a research engineer.
\end{enumerate}

\section{Projects}

\begin{enumerate}
\item \href{https://gitlab.com/Byobe/fast-fm-shad-2019}{Fast factorization machine (\texttt{C++})} \\
  \quad Collaborative project in Yandex School of Data Analysis to implement the following \href{https://www.csie.ntu.edu.tw/~b97053/paper/Rendle2010FM.pdf}{algorithm}
\item \href{https://github.com/deadb0d4/contest}{Coding contests} \\
  \quad My simple routine and small algorithm library for coding contests in \texttt{C++}
\end{enumerate}

\section{Core skills}

\begin{enumerate}
  \item Classical algorithms and data structures
  \item Outstanding level of Mathematics
  \item \texttt{C++} and \texttt{Python 3}
  \item Machine Learning
\end{enumerate}

\end{document}
